First Draft

### 2021-05-05 draft.Rmd
adding references

# Question
•	Question and background information on the data and why you are asking this question(s).  References to previous research/evidence generally would be nice to include. – You must present your question to me during office hours, either next week on  26th or the following week on the 3rd

@@

>>>>

# Question
•	Question and background information on the data and why you are asking this question(s).  References to previous research/evidence generally would be nice to include. – You must present your question to me during office hours, either next week on  26th or the following week on the 3rd  
How can we most accurately predict if someone will have a stroke?

@@

# References
